Spontaneous Droplet Jump with Electro-bouncing

### 2017-06-07 thesis_outline.tex
insulator notes

\section{Notes}
\subsection{Bouncing on thin air}
\subsection{Electric field makes Leidenfrost droplets take a leap}
\subsection{Experimental Determination of the Charge Induced on Water Drops}
\begin{itemize}
\item Use of a ring shaped induction electrode. Droplet charges are a function of the electrode potential, as measured using a pico-ampmeter.
\item The electric field attracts free charge in a continuous conductor, which leads to net charged drops by mass separations (e.g. induced charge) during droplet breakup. This requires that the time interval between breakups is sufficient for charge redistribution in the source liquid. This is distinct from net charge separation by breakup of a electric double layer. So the net charged droplets are the result of the interplay between the external electric field, free charge in a conductive stream, and the Rayleigh-Plateau instability.
\item 
\end{itemize}
\citep{magarvey_experimental_1962}

>>>>

\section{Notes}
\subsection{Bouncing on thin air}
\subsection{Electric field makes Leidenfrost droplets take a leap}
\subsection{Experimental Determination of the Charge Induced on Water Drops}
Some notes from \citep{magarvey_experimental_1962}.
\begin{itemize}
\item Use of a ring shaped induction electrode. Droplet charges are a function of the electrode potential, as measured using a pico-ampmeter.
\item The electric field attracts free charge in a continuous conductor, which leads to net charged drops by mass separations (e.g. induced charge) during droplet breakup. This requires that the time interval between breakups is sufficient for charge redistribution in the source liquid. This is distinct from net charge separation by breakup of a electric double layer. So the net charged droplets are the result of the interplay between the external electric field, free charge in a conductive stream, and the Rayleigh-Plateau instability.
\item 
\end{itemize}

\subsection{Surface voltage and field strength: insulators}
\begin{itemize}
\item For a insulated conductor $A$ with charge $q$, the charge distribute in equilibrium will be such that the field on the interior of the conductor is zero, with field lines being normal to the surface and the integral of the field strength $E$ from any point $P$ in or on the conductor to a ground point $G$ is a constant given by
\[ V = \int^G_P E \dot da \]
where $V$ is the voltage or potential of the conductor.

\end{itemize}
